|

### 2016-04-29 itraquant/Benchmark/itraq-benchmark.Rmd
itraq benchmark

To see if the results coherence, correlation among each ions is computed:
```{r}
cor(qnt.merged$iTRAQ4.114, qnt.merged$Ion_114, method = "spearman", "pairwise.complete.obs")
cor(qnt.merged$iTRAQ4.115, qnt.merged$Ion_115, method = "spearman", "pairwise.complete.obs")
cor(qnt.merged$iTRAQ4.116, qnt.merged$Ion_116, method = "spearman", "pairwise.complete.obs")
cor(qnt.merged$iTRAQ4.117, qnt.merged$Ion_117, method = "spearman", "pairwise.complete.obs")
```

>>>>

To see if the results coherence, correlation among each ions is computed:
```{r}
# Correlation for Ion Reporter 114
cor(qnt.merged$iTRAQ4.114, qnt.merged$Ion_114, method = "spearman","pairwise.complete.obs")
# Correlation for Ion Reporter 115
cor(qnt.merged$iTRAQ4.115, qnt.merged$Ion_115, method = "spearman", "pairwise.complete.obs")
# Correlation for Ion Reporter 116
cor(qnt.merged$iTRAQ4.116, qnt.merged$Ion_116, method = "spearman", "pairwise.complete.obs")
# Correlation for Ion Reporter 117
cor(qnt.merged$iTRAQ4.117, qnt.merged$Ion_117, method = "spearman", "pairwise.complete.obs")
```

# References
